Comparison of Global Solution Methods to a Zero Lower Bound Model

### 2019-04-11 Paper/Paper.tex
Sync Paper to school computers work

\documentclass[12pt, final]{article}
\usepackage{color}
\usepackage{times}
\usepackage{amssymb,amsmath,amsthm}
\usepackage{comment}
\usepackage{dsfont}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage[paperwidth=8.5in,left=1.0in,right=1.0in,top=1.0in,bottom=1.0in,paperheight=11.0in]{geometry}
\usepackage[labelsep=colon,singlelinecheck=false,footnotesize]{caption}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{booktabs}
\usepackage[sort&compress]{natbib}
\usepackage{subfig}
\usepackage{titlesec}
\usepackage[breaklinks]{hyperref}
\hypersetup{pdfdisplaydoctitle=true,bookmarksnumbered=true,colorlinks=true,citecolor=black,linkcolor=darkblue,urlcolor=darkred,pdfstartview=FitH,pdfpagemode=UseNone}
\usepackage[hyphenbreaks]{breakurl}
\usepackage{accents}
\newcommand{\ubar}[1]{\underaccent{\bar}{#1}}

@@

\begin{document}

\section{Model}
\subsection{Firms} The production sector consists of a continuum of monopolistically competitive intermediate goods firms and a final goods firm. Intermediate firm $f \in [0,1]$ produces a differentiated good, $y(f)$, according to $y_t(f) = (k_{t-1}(f))^\alpha(z_tn_t(f))^{1-\alpha}$, where $n(f)$ is the labor hired by firm $f$ and $k(f)$ is the capital rented by firm $f$. $z_t = g_tz_{t-1}$ is technology, which is common across firms. Deviations from the steady-state growth rate, $\bar{g}$, follow
\begin{gather}
  \label{eq:1}
  g_t = \bar{g} + \sigma_g\varepsilon_{g,t},\; \varepsilon_g \sim \mathds{N}(0,1). 
\end{gather}

The final goods firm purchases output from each intermediate firm to produce the final good, $y_t \equiv [\int_{0}^1 y_t(f)^{(\theta-1)/\theta}df]^{\theta/(\theta-1)}$, where $\theta > 1$ is the elasticity of substitution. Dividend maximization determines the demand for intermediate good $f$, $y_t(f) = (p_t(f)/p_t)^{-\theta}y_t$, where $p_t = [\int_{0}^{1} p_t(f)^{1-\theta}df]^{1/(1-\theta)}$ is the price level. Following Rotemberg (1982), intermediate firms pay a price adjustment cost, $adj_t^p(f) \equiv \varphi(p_t(f)/(\bar{\pi}p_{t-1}(f))-1)^2)y_t/2$, where $\varphi > 0$ scales the cost and $\bar{\pi}$ is the steady-state gross inflation rate. Given this cost, firm $f$ chooses $n_t(f)$, $k_{t-1}(f)$, and $p_t(f)$ to maximize the expected discounted present value of future dividends, $E_t\sum_{k=t}^\infty q_{t,k}d_k(f)$, subject to its production function and the demand for its product, where $q_{t,t} \equiv 1$, $q_{t,t+1} \equiv \beta(\lambda_t/\lambda_{t+1})$ is the pricing kernel between periods $t$ and $t+1$, $q_{t,k} \equiv \prod_{j=t+1}^{k>t} q_{j-1,j}$, and $d_t(f) = p_t(f)y_t(f)/p_t - w_tn_t(f) - adj_t^p(f)$. In symmetric equilibrium, the optimality conditions reduce to
\begin{gather}
  y_t = (k_{t-1})^\alpha(z_tn_t)^{1-\alpha},\\
  w_t = (1-\alpha)mc_ty_t/n_t,\\
  r_t^k = \alpha mc_t y_t/k_{t-1},\\
  \varphi(\pi_t^{gap}-1)\pi_t^{gap} = 1-\theta + \theta mc_t + \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)],
\end{gather}
where $\pi^{gap}_t = \pi_t/\bar{\pi}_t$ and $\pi_t = p_t/p_{t-1}$ is the gross inflation rate. If $\varphi = 0$, the real marginal cost of producing a unit of output ($mc_t$) equals $(\theta-1)/\theta$, which is the inverse of the markup of price over marginal cost.
\subsection{Households} The households choose $\{c_t, n_t, b_t, x_t, k_t\}_{t=0}^\infty$ to maximize expected lifetime utility given by $E_0\sum_{t=0}^\infty\beta[\log(c_t-hc^a_{t-1}) - \chi n_t^{1+\eta}/(1+\eta)]$, where $\beta$ is the discount factor, $\chi > 0$ determines steady-state labor, $1/\eta$ is the Frisch elasticity of labor supply, $c$ is consumption, $c^a$ is aggregate consumption, $h$ is the degree of external habit persistence, $b$ is the real value of a privately-issued 1-period nominal bond, $x$ is investment, and $E_0$ is an expectation operator conditional on information available in period 0. The household's budget constraint is given by
\begin{gather*}
    c_t+x_t+b_t/(i_ts_t)=w_tn_t+r_t^kk_{t-1}+b_{t-1}/\pi_t+d_t
  \end{gather*}
where $i$ is the gross nominal interest rate, $r^k$ is the capital rental rate, and $d$ is a real dividend from ownership of intermediate firms. The nominal bond, $b$ is subject to a risk premium, $s$, that follows
\begin{gather}
  \label{eq:6}
  s_t = (1-\rho_s)\bar{s} + \rho_ss_{t-1} + \sigma_s\varepsilon_{s,t},\; 0 \leq \rho_s < 1,\; \varepsilon_s \sim \mathds{N}(0,1),
\end{gather}
where $\bar{s}$ is the steady-state value. An increase in $s_t$ boosts saving, which lowers period-$t$ demand.

@@

\noindent
\textbf{Monetary Policy} The central bank sets the gross nominal interest rate, $i$, according to
\begin{gather}
    \label{eq:15}
    i_t=\max\{1,i_t^n\}\\
      \label{eq:16}
  i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi^{gap}_t)^{\phi_\pi}(y^{g}_{t})^{\phi_y})^{1-\rho_i}\exp(\sigma_i\varepsilon_{i,t}), 0 \leq \rho_i < 1, \varepsilon_i \sim \mathds{N}(0,1),
  \end{gather}
where $y^{gdp}$ is real GDP (i.e., output, $y$, minus the resources lost due to adjustment costs, $adj^p$), $i^n$ is the gross notional interest rate, $\bar i$ and $\bar{\pi}$ are the target values of the inflation and nominal interest rates, and $\phi_\pi$ and $\phi_y$ are the responses to the inflation and output growth gaps. A more negative net notional rate indicates that the central bank is more constrained.\\

@@

\subsection{Parameter Values} \hyperlink{Table 1}{Table 1} shows the model parameters. Parameters are from Atkinson et al. (2019), and were chosen to be characteristic of U.S. data.

\begin{table}
  \hypertarget{Table 1}
  \small
    \setlength{\tabcolsep}{10pt}      
  \begin{tabular}{l c c l c c}
    \hline
  Subjective Discount Factor & $\beta$ & $0.9949$ & Rotemberg Price Adjustment Cost & $\varphi$ & $100$ \\
   Frisch Labor Supply Elasticity & $1/\eta$ & $3$ & Inflation Gap Response & $\phi_\pi$ & $2.0$ \\
  Price Elasticity of Substitution & $\theta$ & $6$ & Output Growth Gap Response & $\phi_y$ & $0.5$ \\
  Steady-State Labor Hours & $\bar{n}$ & $1/3$ & Habit Persistence & $h$ & $0.80$ \\
  Steady-State Risk Premium & $\bar{s}$ & $1.0058$ & Risk Premium Persistence & $\rho_s$ & $0.80$ \\
  Steady-State Growth Rate & $\bar{g}$ & $1.0034$ & Notional Rate Persistence & $\rho_i$ & $0.80$ \\
  Steady-State Inflation Rate & $\bar{\pi}$ & $1.0053$ & Technology Growth Shock SD & $\sigma_g$ & $0.005$ \\
  Capital Share of Income & $\alpha$ & $0.35$ & Risk Premium Shock SD & $\sigma_s$ & $0.005$ \\
  Capital Depreciation Rate & $\delta$ & $0.025$ & Notional Interest Rate Shock SD & $\sigma_i$ & $0.0035$ \\
  Investment Adjustment Cost & $\nu$ & $4$ & & &\\
  \hline
  \end{tabular}
  \caption{Parameter values}
  \label{Tab:1}
\end{table}

\section{Solution Methods}
\subsection{Richter et al. (2014)}
The Richter et al. (2014) solution method is policy function iteration with time iteration and linear interpolation. We first construct an evely-spaced state space by discretizing the endogenous state variables and using the Rouwenhorst (1995) method to approximate the exogenous state variables $s_t$, $g_t$, and $\varepsilon_{i,t}$. As in Richter et al. (2014), we use the Rouwenhorst method so that we do not have to interpolate along the dimensions of the exogenous state variables, providing a faster and more accurate than quadrature methods. To construct the initial policy functions, we solve the log-linear analog of our model with the ZLB not imposed using Sims's (2002) gensys algorithms. We update the policy functions using a fixed point iteration scheme on each node in the discretized state space and calculate the maximum distance between the updated policy functions and the previous guess. Finally, we update the policy functions with our new guess and iterate until the maximum distance is below a convergence criterion. \hyperlink{Appendix B}{Appendix B} provides a more detailed discussion of the solution method. The baseline code for this algorithm is provided as a companion to Richter et al (2014). 
%Add Gust et al solution method
\subsection{Gust et al. (2014)}
The Gust et al. (2014) solution method similarly uses time iteration on a fixed point solution with linear interpolations. Following this solution method, instead of directly computing the policy functions, we estimate smoother functions at and away from the ZLB following Gust, L{\o g}pez-Salido, and Smith (2012) which builds on Christiano and Fisher (2000). Since the policy functions depend directly on the nominal interetst rate, they have a kink or non-differentiability associated with the ZLB.  On the other hand, the regime-indexed policy functions do not depend on the current indicator function and are thus more likely to be smooth. The smoother functions are approximated by specifying:
\begin{gather}
  \textbf{pf}_t(d) = \textbf{pf}_{t,1}(d)\mathds{I}_t(d) + \textbf{pf}_{t,2}(d)(1-\mathds{I}_t(d))
\end{gather}
where $\mathds{I}_t(d)$ is defined by
\begin{gather}
  \mathds{I}_t(d) = 
\begin{cases}
     1 &\text{ if } i_t > 1\\
     0 &\text{ otherwise}
\end{cases}
\end{gather}
The variable $i_t=\max\{1,i_t^n\}$ represents the value of the notional rate derived from evaluating the functions $\textbf{pf}_{t,j}(d)$ for $j \in \{1,2\}$ and using equation (\ref{eq:16}). (For each variable, $j=1$ denotes the function associated with the regime with a positive nominal rate and $j=2$ denotes the function associated with the ZLB regime.) %In calculating the fixed point, we use $i=1$ when the model is in the ZLB regime. 
The functions $\textbf{pf}_{t,j}$ satisfy the residual functions $R_{t,l,j}$ for and $l \in \{1,2,3,4\}$ which correspond to the household FOC bond, FOC capital, FOC investment, and the price Phillips curve, respectively, and $j = 1,2$.
\begin{gather}
  R_{t,1,1} = 1 - s_ti_t\beta E_t[(\lambda_t/\lambda_{t+1})(1/(\bar{\pi}\pi_{t+1}^{gap}))]\\
  R_{t,1,2} = 1 - s_t\beta E_t[(\lambda_t/\lambda_{t+1})(1/(\bar{\pi}\pi_{t+1}^{gap}))]\\
  R_{t,2,j} = q_t - \beta E_t[(\lambda_t/\lambda_{t+1})(r^k_{t+1}+(1-\delta)q_{t+1})]\\
  R_{t,3,j} = 1 - q_t[1-\nu(x^g_t-1)^2/2 - \nu(x_t^g-1)x_t^g] - \nu\beta\bar{g}E_t[q_{t+1}(\lambda_t/\lambda_{t+1})(x^g_{t+1})^2(x^g_{t+1}-1)]\\
  R_{t,4,j} = \varphi(\pi_t^{gap}-1)\pi_t^{gap} - (1-\theta) - \theta mc_t - \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)]
  \end{gather}

>>>>

\documentclass[12pt, final]{article}
\usepackage{color}
\usepackage{times}
\usepackage{amssymb,amsmath,amsthm}
\usepackage{comment}
\usepackage{dsfont}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage[paperwidth=8.5in,left=1.0in,right=1.0in,top=1.0in,bottom=1.0in,paperheight=11.0in]{geometry}
\usepackage[labelsep=colon,singlelinecheck=false,footnotesize]{caption}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{booktabs}
\usepackage[sort&compress]{natbib}
\usepackage{subfig}
\usepackage{titlesec}
\usepackage[breaklinks]{hyperref}
\hypersetup{pdfdisplaydoctitle=true,bookmarksnumbered=true,colorlinks=true,citecolor=black,linkcolor=darkblue,urlcolor=darkred,pdfstartview=FitH,pdfpagemode=UseNone}
\usepackage[hyphenbreaks]{breakurl}
\usepackage{accents}
\newcommand{\ubar}[1]{\underaccent{\bar}{#1}}
\usepackage{epstopdf}
\epstopdfsetup{outdir=./}
\usepackage{xcolor}
\usepackage{setspace}
\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist 
\newcommand{\forceindent}{\leavevmode{\parindent=15pt\indent}}

@@

\title{Comparison of Global Solution Methods to a Zero Lower Bound Model}
\date{\small First Draft: \today}
\author{Emily Martell\thanks{Thank you to Professor Throckmorton for advising and providing materials for this project. Thank you to Professor Campbell, Professor Han, Professor Rolek, and Professor Throckmorton for serving on my committee.}}
\begin{document}
\maketitle
\bigskip
\begin{center}
\fontsize{14pt}{\baselineskip}\sc Abstract%\normalfont
\end{center}

\onehalfspacing
\begin{changemargin}{1cm}{1cm}

{\small \forceindent During the Great Recession, the U.S. Federal Reserve lowered policy rates to zero, creating a kink in its policy rule, and calling into question traditional solution methods. Recent work has explored fully nonlinear models to represent the ZLB, but not much work has compared the performance of different solution methods. Two suggested solution methods are linear interpolation This paper examines the effect of making the policy functions conditional on whether the ZLB binds. We consider a fully nonlinear New Keynesian model with capital, and a solution algorithm with policy function iteration and linear interpolation. We find no evidence that the regime-indexed policy functions are smoother. In addition, the solution algorithms perform similarly with respect to accuracy, but the solution containing the regime-indexed policy functions is much slower, all else equal.}
\end{changemargin}
\vfill
\pagebreak

\section{Introduction}

As a result of the global financial crisis of 2007-9 and the subsequent recession, central banks lowered
their policy rate to its zero lower bound (ZLB). Although the ZLB constraint has always existed,
for most of the data prior to the recession, policy rates were well above zero. In the wake of this
unprecedented lowering of policy rates, the ZLB holds for a considerable portion of historic data
for three major economies --- the US, Japan, and the Euro Area. The ZLB creates a kink in the policy
rule and calls into question linear estimation methods.

Researchers have responded to this inherent
nonlinearity in different ways. Some have failed to incorporate the ZLB period data. Others have
chosen to estimate linear models on the entire data set; however, this could lead to inaccurate estimates
of model parameters and model predictions. Some have estimated a piecewise linear version of the nonlinear model (e.g., \hyperlink{Guerrieri}{\color{black}{Guerrieri and Iacoviello, 2017}}). A few have estimated fully nonlinear models that treats the
	ZLB as an occasionally binding constraint (e.g., \hyperlink{Gust}{\color{black}{Gust et al.,\ 2017}}; \hyperlink{Plante}{\color{black}{Plante et al.,\ 2018}}; \hyperlink{RT}{\color{black}{Richter and Throckmorton, 2016}}). These papers solve the nonlinear model using projection methods, which is explored in several other papers (e.g. \hyperlink{Aruoba}{\color{black}{Aruoba et al.,\ 2018}}; \hyperlink{Fernandez}{\color{black}{Ferna\'ndez-Villaverde et al.,\ 2015)}}. Solving a nonlinear model using projection methods provides the most comprehensive treatment of the ZLB but is computationally intensive.

As it is important to incorporate all historical data and yield accurate parameter values and predictions, the path forward seems to be in fully nonlinear models. Among those that use projection methods to solve a nonlinear model, some use policy function iteration with linear interpolation (e.g., \hyperlink{Plante}{\color{black}{Plante et al.,\ 2018}}; \hyperlink{RT}{\color{black}{Richter and Throckmorton, 2016}}). In terms of the approximating function, others estimate alternative functions like regime-indexed policy functions (\hyperlink{Gust}{\color{black}{Gust et al.,\ 2017}}) or piecewise smooth policy functions (\hyperlink{Aruoba}{\color{black}{Aruoba et al.\ 2018}}) to avoid the kink introduced by the ZLB.  With respect to the grid construction, some use the Smolyak collocation method developed by \hyperlink{Judd}{\color{black}{Judd et al.\ (2010)}} to reduce the burden of dimensionality (e.g., \hyperlink{Gust}{\color{black}{Gust et al.,\ 2017}}; \hyperlink{Fernandez}{\color{black}{Ferna\'ndez-Villaverde et al.\, 2015}}; \hyperlink{Aruoba}{\color{black}{Aruoba et al.,\ 2018}}).
Not much work has been done in comparing the accuracy and speed of different global nonlinear solution methods. We will  examine the performance of \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}} and \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} in terms of accuracy and speed as examples of different ways to solve nonlinear models.

The \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}} solution method is policy function iteration with linear interpolation to approximate future variables.  The state space features evenly-spaced nodes and exogenous state variables  approximated with the Markov chain from \hyperlink{Rouwenhorst}{\color{black}{Rouwenhorst (1995)}}. The Rouwenhorst approximation is useful because it only requires interpolation along the dimensions of the endogenous state variables. This yields a faster and more accurate solution than quadrature methods.They update the policy functions with linear interpolation to accurately capture the kink experienced at the ZLB.

The \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} solution method approximates policy functions underlying the model's decision rule using an antistropic Smolyak method with Chebyshev polynomials. (See \hyperlink{Judd2}{\color{black}{Judd et al.\ (2014)}} for a discussion of antistropic Smolyak methods). They approximate the exogenous state variables using Gauss-Hermite quadrature. Instead of directly computing the policy functions, they estimate functions at and away from the ZLB, which builds on \hyperlink{Christiano}{\color{black}{Christiano and Fisher (2000)}}. The idea is that the policy functions feature a kink or non-differentiability at the ZLB and regime-indexing the policy functions will yield smoother functions.

In this paper, we consider the effect of making the policy functions conditional on whether the ZLB binds. To isolate the effect of splitting the policy functions, we use policy function iteration on a fixed point with linear interpolation following \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}}. This solution method also provides the motivation for a single policy function, and the \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} solution provides the motivation for a regime-indexed policy function. Henceforth, the solution method based on the \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}} solution algorithm will be denoted ART and the solution algorithm that estimates smoother functions based on \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} will be denoted GHLS. It is important to note that we do not consider the effect of a Smolyak basis with Chebyshev polynomials, so this is a modified \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} solution method. The key point in this paper is to explore how splitting up the policy functions conditional on the ZLB impacts the speed and accuracy of the solution of a nonlinear model.

First, we construct the state space with evenly-spaced nodes and approximate the exogenous state variables with \hyperlink{Rouwenhorst}{\color{black}{Rouwenhorst (1995)}}. After obtaining initial conjectures for a set of policy functions from the log-linear solution, we iterate on the policy functions, linearly interpolating and numerically integrating the policy functions each step, using a fixed point iteration scheme. The algorithm converges once the maximum distance between successive guesses of policy functions falls below a convergence criterion. For the ART portion, we update a single policy function. For the GHLS portion, we update regime-indexed policy functions.

%In a NK model instead???
The standard representation of the Euler equation is
\begin{gather*}
u'(c_t)  = \beta u'(c_{t+1})[f'(k_{t+1}) + 1 - \delta],
\end{gather*}
where $u(\cdot)$ is the instantaneuous utility function, $0<\beta<1$ is the discount factor, $c_t$ is consumption at period $t$, $k_t$ is the capital stock at the beginning of the period, $0 < \delta \leq 1$ is the rate of depreciation, and $f(\cdot)$ is the production function. $u(\cdot)$ and $f(\cdot)$ are differentated according to the choice variables. The Euler equation is the fundamental dynamic equation in intertemporal optimization problems that include dynamic constraints. It states that the marginal cost of forgoing consumption today must equal the discounted marginal benefit of investing in capital for one period.   %Cite Dr Richter's notes?

%Here make a better segway
The interest rate appears in the household's budget constraint in models where the household has the choice of owning a nomimal bond. The household must choose a combination of consumption, labor, and bond holdings to maximize expected lifetime utility. Thus, the household's choice of consumption depends on the interest rate and whether the economy is at the ZLB. To approximate regime-indexed consumption policy functions $c_t^{ZLB}$ and $c_t^{normal}$, we provide initial guesses based on the log-linear solution. We refine the policy function guesses as follows: For each node in the state space, we solve for the time $t$ variables with either the $c_t^{ZLB}$  or $c_t^{normal}$ according to $i_t$, the interest rate at time $t$. With the time $t$ variables, we linearly interpolate both policy functions. Next, we calculate the interest rate on each node in the state space, construct an aggregate consumption policy function based on whether the economy is at the ZLB on each node, and calculate time $t+1$ variables acordingly. We then update $c_t^{ZLB}$ with an interest rate of 1, and $c_t^{normal}$ with $i_t$.

%It might help to explain in the intro the key difference in the approximation of the policy functions. You could show a standard Euler Equation, point out the nominal interest rate, and then explain you would approximate a policy function for consumption that depends on whether the economy is at the ZLB.

In terms of accuracy, both the ART and GHLS yield similar Euler equation errors, with ART being slightly more accurate for the model with capital. The ART method converges much more quickly than the GHLS method, particularly when capital is introduced to the model. There is not a clear advantage of the regime-indexed policy function approximation when using an evenly spaced grid with linear interpolation. All else equal, using regime-indexed policy functions increases the computing time. However, introducing Chebyshev polynomials and sparse grid methods as in \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} may reduce solution time and allow us to solve larger models with more state variables. Further research could explore how much accuracy is gained or lost relative to using non regime-indexed policy functions approximated with Chebyshev polynomials.

The remainder of the paper is as follows: \hyperlink{Section 2}{Section 2} outlines our setup for the model with capital. \hyperlink{Section 3}{Section 3} describes regime-indexed polynomials and outlines the solution algorithm. \hyperlink{Section 4}{Section 4} discusses the results in terms of solution time, curvature of policy functions, and Euler equation errors. \hyperlink{Section 5}{Section 5} concludes.

\section[Section 2]{Model \hypertarget{Section 2}{}} 
This is a widely-employed New Keynesian model which is similar to the model in \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}}, but includes capital accumulation as in \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}}. Thus, it is an appropriate model to benchmark the accuracy and speed of the two solution methods.

\subsection{Firms} The production sector consists of a continuum of monopolistically competitive intermediate goods firms and a final goods firm. Intermediate firm $f \in [0,1]$ produces a differentiated good, $y(f)$, according to $y_t(f) = (k_{t-1}(f))^\alpha(z_tn_t(f))^{1-\alpha}$, where $n(f)$ is the labor hired by firm $f$ and $k(f)$ is the capital rented by firm $f$. $z_t = g_tz_{t-1}$ is technology, which is common across firms. Deviations from the steady-state growth rate, $\bar{g}$, follow
\begin{gather}
  \label{eq:1}
  g_t = \bar{g} + \sigma_g\varepsilon_{g,t},\; \varepsilon_g \sim \mathds{N}(0,1). 
\end{gather}

The final goods firm purchases output from each intermediate firm to produce the final good, $y_t \equiv [\int_{0}^1 y_t(f)^{(\theta-1)/\theta}df]^{\theta/(\theta-1)}$, where $\theta > 1$ is the elasticity of substitution. Dividend maximization determines the demand for intermediate good $f$, $y_t(f) = (p_t(f)/p_t)^{-\theta}y_t$, where $p_t = [\int_{0}^{1} p_t(f)^{1-\theta}df]^{1/(1-\theta)}$ is the price level. Following \hyperlink{Rotemberg}{\color{black}{Rotemberg (1982)}}, intermediate firms pay a price adjustment cost, $adj_t^p(f) \equiv \varphi(p_t(f)/(\bar{\pi}p_{t-1}(f))-1)^2)y_t/2$, where $\varphi > 0$ scales the cost and $\bar{\pi}$ is the steady-state gross inflation rate. Given this cost, firm $f$ chooses $n_t(f)$, $k_{t-1}(f)$, and $p_t(f)$ to maximize the expected discounted present value of future dividends, $E_t\sum_{k=t}^\infty q_{t,k}d_k(f)$, subject to its production function and the demand for its product, where $q_{t,t} \equiv 1$, $q_{t,t+1} \equiv \beta(\lambda_t/\lambda_{t+1})$ is the pricing kernel between periods $t$ and $t+1$, $q_{t,k} \equiv \prod_{j=t+1}^{k>t} q_{j-1,j}$, and $d_t(f) = p_t(f)y_t(f)/p_t - w_tn_t(f) - adj_t^p(f)$. In symmetric equilibrium, the optimality conditions reduce to
\begin{gather}
  y_t = (k_{t-1})^\alpha(z_tn_t)^{1-\alpha},\\
  w_t = (1-\alpha)mc_ty_t/n_t,\\
  r_t^k = \alpha mc_t y_t/k_{t-1},\\
  \varphi(\pi_t^{gap}-1)\pi_t^{gap} = 1-\theta + \theta mc_t + \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)],
\end{gather}
where $\pi^{gap}_t = \pi_t/\bar{\pi}_t$ and $\pi_t = p_t/p_{t-1}$ is the gross inflation rate. If $\varphi = 0$, the real marginal cost of producing a unit of output ($mc_t$) equals $(\theta-1)/\theta$, which is the inverse of the markup of price over marginal cost.
\subsection{Households} The households choose $\{c_t, n_t, b_t, x_t, k_t\}_{t=0}^\infty$ to maximize expected lifetime utility given by $E_0\sum_{t=0}^\infty\beta[\log(c_t-hc^a_{t-1}) - \chi n_t^{1+\eta}/(1+\eta)]$, where $\beta$ is the discount factor, $\chi > 0$ determines steady-state labor, $1/\eta$ is the Frisch elasticity of labor supply, $c$ is consumption, $c^a$ is aggregate consumption, $h$ is the degree of external habit persistence, $b$ is the real value of a privately-issued 1-period nominal bond, $x$ is investment, and $E_0$ is an expectation operator conditional on information available in period 0. The household's budget constraint is given by
\begin{gather*}
    c_t+x_t+b_t/(i_ts_t)=w_tn_t+r_t^kk_{t-1}+b_{t-1}/\pi_t+d_t,
  \end{gather*}
where $i$ is the gross nominal interest rate, $r^k$ is the capital rental rate, and $d$ is a real dividend from ownership of intermediate firms. The nominal bond, $b$ is subject to a risk premium, $s$, that follows
\begin{gather}
  \label{eq:6}
  s_t = (1-\rho_s)\bar{s} + \rho_ss_{t-1} + \sigma_s\varepsilon_{s,t},\; 0 \leq \rho_s < 1,\; \varepsilon_s \sim \mathds{N}(0,1),
\end{gather}
where $\bar{s}$ is the steady-state value. An increase in $s_t$ boosts saving, which lowers period-$t$ demand.

@@

\noindent
\textbf{Monetary Policy} The central bank sets the gross nominal interest rate, $i$, according to
\begin{gather}
    \label{eq:15}
    i_t=\max\{1,i_t^n\},\\
      \label{eq:16}
  i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi^{gap}_t)^{\phi_\pi}(y^{g}_{t})^{\phi_y})^{1-\rho_i}\exp(\sigma_i\varepsilon_{i,t}), 0 \leq \rho_i < 1, \varepsilon_i \sim \mathds{N}(0,1),
  \end{gather}
where $y^{gdp}$ is real GDP (i.e., output, $y$, minus the resources lost due to adjustment costs, $adj^p$), $i^n$ is the gross notional interest rate, $\bar i$ and $\bar{\pi}$ are the target values of the inflation and nominal interest rates, and $\phi_\pi$ and $\phi_y$ are the responses to the inflation and output growth gaps. A more negative net notional rate indicates that the central bank is more constrained.\\

@@

\begin{table}[H]
  \hypertarget{Table 1}
\centering
\captionsetup{justification=centering}
  \small
    \setlength{\tabcolsep}{7.5pt}      
  \begin{tabular}{l c c l c c}
    \hline
  Subjective Discount Factor & $\beta$ & $0.9949$ & Rotemberg Price Adjustment Cost & $\varphi$ & $100$ \\
   Frisch Labor Supply Elasticity & $1/\eta$ & $3$ & Inflation Gap Response & $\phi_\pi$ & $2.0$ \\
  Price Elasticity of Substitution & $\theta$ & $6$ & Output Growth Gap Response & $\phi_y$ & $0.5$ \\
  Steady-State Labor Hours & $\bar{n}$ & $1/3$ & Habit Persistence & $h$ & $0.80$ \\
  Steady-State Risk Premium & $\bar{s}$ & $1.0058$ & Risk Premium Persistence & $\rho_s$ & $0.80$ \\
  Steady-State Growth Rate & $\bar{g}$ & $1.0034$ & Notional Rate Persistence & $\rho_i$ & $0.80$ \\
  Steady-State Inflation Rate & $\bar{\pi}$ & $1.0053$ & Technology Growth Shock SD & $\sigma_g$ & $0.005$ \\
  Capital Share of Income & $\alpha$ & $0.35$ & Risk Premium Shock SD & $\sigma_s$ & $0.005$ \\
  Capital Depreciation Rate & $\delta$ & $0.025$ & Notional Interest Rate Shock SD & $\sigma_i$ & $0.0035$ \\
  Investment Adjustment Cost & $\nu$ & $4$ & & &\\
  \hline
  \end{tabular}
  \caption{Parameter values}
  \label{Tab:1}
\end{table}

\subsection{Parameter Values} \hyperlink{Table 1}{Table 1} shows the model parameters. Parameters are from \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}}, and are chosen to be characteristic of U.S. data. The subjective discount factor, $\beta$ is set to $0.9949$, the time average of the values implied by the steady-state consumption Euler equation and the federal funds rate. The Frisch labor supply elasticity $1/\eta$ is set to 3 to match the macro estimate in \hyperlink{Peterman}{\color{black}{Peterman (2016)}}. The price elasticity of substitution $\theta$ is set to 6, matching GHLS and corresponding to to a 20\% average markup. Steady-state labor hours $\bar{n}$ is set to 1/3 of available time. The steady-state risk premium, growth rate, and inflation rate are set to the time averages of per capital real DGP growth, the percent GDP implicit price deflator, and the Baa corporate bond yield relative to the yield on the 10-Year Treasury. The capital share of income $\alpha$ is equal to the \hyperlink{Fernald}{\color{black}{Fernald (2012)}} utilization-adjusted quarterly-TFP estimates of the capital share of income from 1988-2017Q4. The other parameters are set to values consistent with posterior estimates from similar models in the literature. For the model without capital, all parameters are the same except $\sigma_i$ which is set to $0.002$. (For the model with capital, $\sigma_i$ was originally set to $0.002$ to match \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}}, but the model failed to hit the ZLB during simulation, so we increased the parameter to $0.0035$.)

\section[Section 3]{Solution Methods \hypertarget{Section 3}{}} 
\subsection{Regime-indexed policy functions} Instead of directly approximating the policy functions, some papers elect to approximate alternative functions to avoid the kink experienced at the ZLB (e.g., \hyperlink{Gust}{\color{black}{Gust et al.,\ 2017}}; \hyperlink{Aruoba}{\color{black}{Aruoba et al.,\ 2018}}). \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} uses policy functions that are indexed by the interest-rate regime. Because these functions do not depend on the current indicator function,\hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} claims that they are more likely to be smooth. The regime-specific functions still depend on a secondary effect that the non-differentiability in the nominal rate in the following period has on expectations of future variables.  However, following \hyperlink{Christiano}{\color{black}{Christiano and Fisher (2000)}} this effect should be small due to the presence of the expectations operators which act to smooth out regime-specific functions. The idea for regime-indexed policy functions is as follows:
\begin{gather}
    \label{eq:18}
  \textbf{pf}_t(d) = \textbf{pf}_{t,1}(d)\mathds{I}_t(d) + \textbf{pf}_{t,2}(d)(1-\mathds{I}_t(d)),
\end{gather}
